Weather Data Integration and Assimilation System\\

### 2020-02-21 Paper.tex
Paper finished with summary

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.8\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
    \caption{Load testing with auto-scaling import ascii grid number of pods over time.}
    \label{pfi:obs_all_auto_15m_import_grid_pod}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Performance Metrics Analysis}
\label{psubse:performance_metrics}
\paragraph{Latency}
The latency for each operation type kept constant over the whole test plan run time without any significant change. When the request size increased from 24 data points to 96 data points, the latency increase throughout the whole test plan with a smaller number. But for each test run the latency kept constant over the time.
During the \cref{subse:obs_test_plan_all_auto_15min} test run, the performance of the Grid data got better when compared to the \cref{subse:obs_test_plan_all_15min}. Which means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.

\paragraph{Throughput}
While keeping the latency constant without significant change, the throughput of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector and Grid.
When number of active threads increased, the \acrshort{wdias} able to provide the same throughput with maintaining the latency stable.

One of the reason to having deviations at the peak time due to use of single instance for the data consistency such as \acrshort{influxdb} for Scalar and Vector data, and netCDF with parallel support for Grid data. Further it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}. With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.

Adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled. This has some performance issues as well as memory leak issues. Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN.
Other than \acrshort{eks}, if users can use a \acrshort{k8s} cluster which support Persistent Volumes with the access of Read Write  Many \cite{LinuxFoundationPersistentKubernetes} , then it is possible to run multiple pods of adapter-grid and increase the throughput of the \acrshort{wdias}.

\paragraph{Resource Utilization}
Since \acrshort{wdias} using the \acrshort{k8s} as the container orchestration system, it allows to scale up and cool down the system as required based on the workload. This demonstrate on the test plan of \cref{subse:obs_test_plan_all_auto_15min}, and the system get scale up to the maximum at the peak time. Then cool down to single pod after finishing the test cases.
Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs. As described in the \cref{se:microservice}, it uses the many of the concept of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

\paragraph{Auto Scaling}
The \acrshort{wdias} supports auto-scaling by out of the box with \acrshort{k8s}. Services can configure with maximum number of pods in order to avoid over resource usage. When there is not much workload on the system, system cool down to less pods in order to save more resources. When there is any issue with a pod, \acrshort{k8s} auto schedule another pod and remove the unhealthy pod. Also it allows to update the system without any down time with rollback updates.

\paragraph{Risk of Unable to Process Data}
During the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with lower rate of failures to process the requests, mainly with insert Grid data. If the usage of \acrshort{wdias} want to reduce the risk of unable to process data, then system can configure to run with redundant pods in order to handle spike of workloads. Also while configure for the auto-scaling, the \acrshort{k8s} can configure to maintain lower amount of CPU usage such as 50\% to 60\% rather 80\%. Such configuration with always spawn new pods to handle double of current peak load.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Strengths and Limitations}
\label{psubse:limitations}
\dbc{Make this the dicussion and a sub-section of Sec. 4}

\paragraph{Lack of data preprossessing modules}
The extension module enable plugin system to integrate prepossessing modules which can use for process the data which are inserted to the system or based on regular intervals. Also \acrshort{wdias} provide a more generic open interface approach to create more preprocessing modules. Since \acrshort{wdias} is an open source system, it expect more modules to be create by the community. When compared to other system like \acrshort{fews}, current system only have few extension for the testing purpose. This is one of the major area that need to be improved.

\paragraph{Supporting Irregular Grids}
At the moment \acrshort{wdias} does not support Irregular Grids, but it has the API endpoints define for the implementation which can follow the same microservice architecture. The scope of the \acrshort{wdias} does not belong such level of implementation and the scope has reduced by removing such components from the system.

\paragraph{Grid data performance}
As mentioned in the \cref{se:conclusion}, the adapter-grid is using a Python wrapper for netCDF FORTRAN implementation with parallel IO enabled. This has some performance issues as well as memory leak issues. Since each microservice in the \acrshort{wdias} independent of technology that can use to implement the service, it will increase the performance if the adapter-grid directly ported to netCDF with a low level language such as C or FORTRAN. They are some future work that can focus on improving the performance of grid data.

\paragraph{Define infrastructure as code}
Physical nodes for the \acrshort{k8s} cluster created using Cloud Computing provider such as \acrshort{eks}. And defining the each pod resource limitations at the helm chart level. But the infrastructure that need to deploy the \acrshort{wdias} can define as code such as using tools like Teraform which is independent of the Cloud Computing provider. Using such tool, users will able to easy deploy the \acrshort{wdias} on any Cloud provider without much hassle.

\paragraph{Further improve hierarchical database performance}
As further described in \cref{se:conclusion}, it is possible to increase the performance of these bottlenecks much higher such as using \acrshort{influxdb} Commercial cluster support for high availability or horizontal scaling of \acrshort{influxdb}. With \acrshort{influxdb} cluster, it is possible to run multiple pods of adapter-scalar and adapter-vector for support more server hits per second.
Other than that, the \acrshort{wdias} performance can improve via partitioning the timeseries key space into multiple \acrshort{influxdb} instances. The adapter-scalar or adapter-vector can improve to plug multiple instance of \acrshort{influxdb} instances by changing the configurations. As an example, based on the key attribute \cref{subse:timeseries_key_attributes} Timeseries Type, the adapter-scalar can connect to four instance of \acrshort{influxdb} instances such as  External Historical, External Forecast, Simulated Historical, and Simulated Forecast etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\label{pse:summary}
\dbc{Summary is too long. Should not be more than a single para}
To enhance the accuracy of the weather prediction, it is required to have reliable weather data for \acrshort{nwm}. Most of existing weather data systems are proprietary or close sourced, or not up to date with the existing cloud computing technologies.
We proposed an extendable open source Weather Data Integration and Assimilation Systems which is known as \acrshort{wdias}. It focused on providing efficiently integrates weather data from different sources with quality control and supporting steaming large size of data. And compatible with current cloud computing technologies and architecture patterns.

First the architecture starts with SOA using a \acrfull{esb}, and then moved to Actor model based architecture. After comparing the disadvantages of using such architecture with the system requirements, final architecture come up with modern microservice architecture.
Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure in order to provide higher performance while store the weather data. The system uses \acrshort{influxdb} timeseries database for storing Scalar and Vector timeseries data, and using \acrshort{netCDF} for storing Grid timeseries data.
Also the system provide a generic open mechanism to integrate new modules as extension in order to enhance the features of the system. This capability enable to integrate weather data preprocessing flows as extension modules.
The extension API provide easy access to create and modify the extension triggers on the fly without stopping the system or any downtime in order to change the configurations.
The system provides extensive timeseries query endpoints to easy search over the system timeseries metadata with supporting Geo based queries.

\acrshort{wdias} performance test is perform using the \acrshort{jmeter} tool's distributed testing capabilities which separately testing each modules. Then the test plans are performed with increasing the request size, and monitored the performance metrics. The system is setup on the \acrfull{eks} as per the configurations of \cref{subse:test_sys_config}.
During the performance test plans, the system were able to provide constant throughput by keeping the latency constant while increasing the workload. Which exhibit the scalability of the system.
With the \acrshort{k8s} auto-scaling, the \acrshort{wdias} were able to elastically adjust the number of pods according to the workload with the given configurations.

>>>>

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{results/obs/all_auto/obs_all_auto_15m_import_grid_pod.png}
    \caption{Load testing with auto-scaling import ascii grid number of pods over time.}
    \label{pfi:obs_all_auto_15m_import_grid_pod}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Performance Metrics Analysis}
\label{psubse:performance_metrics}

The \emph{Latency} for each operation type kept constant over the whole test plan run time without any significant change. When the request size increased from 24 data points to 96 data points, the latency increase throughout the whole test plan with a smaller number. But for each test run, the latency kept constant over time.
During the \cref{ptab:obs_all_auto_15_min_summary_throughput} test run, the performance of the Grid data got better when compared to \cref{ptab:obs_all_15_min_summary_throughput}. This means by adding more resources to the \acrshort{wdias}, it can handle more workload on the system.

While keeping the latency constant without significant change, the \emph{throughput} of the \acrshort{wdias} kept constant while increasing the request size from 60min data (24 data points) to 15min data (96 data points) for all the data types such as Scalar, Vector, and Grid.
When the number of active threads increased, the \acrshort{wdias} able to provide the same throughput with maintaining the latency stable.

One of the reasons for having deviations at the peak time due to uses of single instance for the data consistency such as \acrshort{influxdb} for Scalar and Vector data, and netCDF with parallel support for Grid data. Further, it is possible to gain more performance using the databases with configure with high scalability and high availability features such as Sharding and Replication.

When looking into the \emph{resource utilization} of \acrshort{wdias}; since it is using the \acrshort{k8s} as the container orchestration system, it allows us to scale up and cool down the system as required based on the workload. This demonstrates the test plan of \cref{subse:obs_test_plan_all_auto_15min}, and the system gets scale up to the maximum at the peak time. Then cool down to a single pod after finishing the test cases.
Given above \acrshort{wdias} can run from 1 CPU node to nodes with 100 CPUs. As described in the \cref{psubse:microservice_architecture}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

The \acrshort{wdias} supports \emph{auto scaling} by out of the box with \acrshort{k8s}. Services can configure with a maximum number of pods to avoid over resource usage. When there is not much workload on the system, the system cools down to fewer pods to save more resources. When there is an issue with a pod, \acrshort{k8s} auto-schedule another pod and remove the unhealthy pod. Also, it allows updating the system without any downtime with rollback updates.

\emph{Risk of unable to process data} during the test performance, the \acrshort{wdias} processed many requests with higher request size than the normal usage with a lower rate of failures to process the requests, mainly with insert Grid data. If the usage of \acrshort{wdias} wants to reduce the risk of unable to process data, then the system can configure to run with redundant pods to handle spike of workloads. Also while configuring for the auto-scaling, the \acrshort{k8s} can configure to maintain a lower amount of CPU usage such as 50\% to 60\% rather  than 80\%. Such configuration with always spawn new pods to handle double of current peak load.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Strengths and Limitations}
\label{psubse:limitations}
\dbc{Make this the discussion and a sub-section of Sec. 4}

As we showed that the \acrshort{wdias} can perform better, there are some improvements that can add to improve the performance and usability of the system.

\emph{Lack of data preprocessing modules}:
The extension module enables the plugin system to integrate prepossessing modules that can use for process the data which are inserted to the system or based on regular intervals. Also, \acrshort{wdias} provides a more generic open interface approach to create more preprocessing modules. Since \acrshort{wdias} is an open-source system, it expects more modules to be created by the community. When compared to other systems like \acrshort{fews}, the current system only have few extensions but it is more easy to add new extensions compared to other systems.

Improve the \emph{Grid data performance} by porting \acrshort{netCDF} C or FORTRAN implementation with adapter-grid rather using a Python wrapper. Using tools like Terraform which is independent of the Cloud Computing provider \emph{define \acrshort{wdias} infrastructure as code}, then users will able to easily deploy the \acrshort{wdias} on any Cloud provider without much hassle. \emph{Tune \acrshort{wdias} database structure performance} with using Z-axis scaling. Some of other features are alerting extension modules, publisher subscriber capabilities via extension modules, supporting irregular Grids.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
\label{pse:summary}
\dbc{Summary is too long. Should not be more than a single para}
\hl{Just kept the important sections}

Even though there are many weather data integration systems, most of them are proprietary or closed source and based on basic client-server architectures or monolithic distributed system architectures. Thus those are unable to get the advantage of modern computational models such as containerized applications and using the could computing to gain benefits of scalability, high availability and low-cost operations.
Also for an island like Sri Lanka that having different kinds of weather seasons over the year those software needs to be highly customized. In this paper, we present an extendable open source weather data integration and assimilation system known as \acrshort{wdias} which uses modern microservice architecture pattern and cloud computing tools such as container orchestration to gain high scalability and availability.

Based on the nature of the weather metadata, the \acrshort{wdias} used a database structure to provide higher performance while storing the weather data optimum.
As described in \cref{pse:wdias_architecture}, it uses many of the concepts of microservice architecture to create stateless, failover, redundant microservice. Also, the system provides a generic open mechanism to integrate new modules as an extension to enhance the features of the system and weather data preprocessing. The \acrshort{wdias} provides an extension API to easy access to create and modify the extension triggers on the fly and support complex timeseries metadata queries with Geo-based support.

The paper also presents performance analysis of the \acrshort{wdias} with load testing using \acrshort{jmeter} tool with system setup on \acrfull{k8s} cluster on Cloud infrastructure. Based on the observations, the system was able to handle 300 \acrshort{rps} (which means 18,000 requests per minute) successfully with minimizing the error rate to zero. Also, while increasing the request size, the system was able to perform the same while keeping the latency constant without any significant change and the system was able to increase the throughput by keeping the latency constant while increasing the workload which exhibits the scalability of the system.
With the \acrshort{k8s} auto-scaling, the \acrshort{wdias} were able to elastically adjust the number of pods to handle the workload and shows that the system can run from 1 CPU node to nodes with a few hundred CPUs.

### 2020-02-21 summary/sec_1-conclusions.tex
Paper finished with summary

Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of hierarchical database structure to provide higher performance while storing the weather data optimum. The system uses a timeseries database for storing Scalar and Vector timeseries data and using \acrshort{netCDF} for storing Grid timeseries data. And each database adapter uses the concept of database per service which allows each microservice service to scale without interference from other microservices.
And it uses microservice sagas pattern for asynchronous data handling for requests with higher size. According to the \cref{se:microservice}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.

>>>>

Based on the microservice architecture patterns and the nature of the weather metadata, the \acrshort{wdias} came up with the idea of database structure to provide higher performance while storing the weather data optimum. The system uses a timeseries database for storing Scalar and Vector timeseries data and using \acrshort{netCDF} for storing Grid timeseries data. And each database adapter uses the concept of database per service which allows each microservice service to scale without interference from other microservices.
And it uses microservice sagas pattern for asynchronous data handling for requests with higher size. According to the \cref{se:microservice}, it uses many of the concepts of modern microservice architecture to create stateless, failover, redundant microservice to achieve such capabilities.
